Globally-centered autocovariances in MCMC

### 2020-08-20 Paper/main.tex
Only left with Sensor netwrok example now.

An important method of assessing the reliability of $\bar{\bar{Y}}$ in estimating $\mu_g$ is to simulate until a desired effective sample size (ESS) is obtained. ESS are number of independent and identically distributed samples that would yield the same Monte Carlo variability as this correlated sampler for estimating $\mu_g$. Let $|\cdot|$ denote determinant. A multiple chain version of the ESS as defined by \cite{vats2019multivariate} is
\[
\textrm{ESS} = mn \left(\dfrac{|\Upsilon(0)|}{|\Sigma|}\right)^{1/p}\, .
\]

@@

There are only a handful of MCMC methods where the true autocovariance and asymptotic variance are known in closed form. To compare the globally and locally-centered estimators when the truth is known, we use a slowly mixing vector autoregressive process of order 1 (VAR(1)). We want to deliberately make the Markov chains explore the sample space slowly. Consider a $p$-dimensional VAR(1) process $\{X_t\}_{t \geq 1}$ such that
%
\[
X_t = \Phi X_{t-1} + \epsilon_t
\]

where $X_t \in \mathbb{R}^p$, $\Phi $ is a $p \times p $ matrix, $ \epsilon_t \overset{i.i.d.}{\sim} N(0, \Omega)$, and $\Omega$ is a positive definite $p \times p$ matrix. The invariant distribution for this Markov chain is $N(0, \Psi)$ where $\mathcal{N}(.,.)$ stands for the Gaussian distribution. The lag-k autocovariance $\Gamma(k)$ can be calculated for $k >0$ as $\Gamma(k) = \Phi^k\Psi \textrm{ and } \Gamma(-k) = \Psi(\Phi^T)^k$. The Markov chain is geometrically ergodic when the spectral norm of $\Phi$ is less than 1 (\cite{10.2307/1427459}). The CLT holds for the invariant distribution, therefore, $\Sigma$ exists and is known in closed form.

Let $\phi_{\max}$ be the largest absolute eigenvalue of $\Phi$ such that $\abs{\phi_{\max}} < 1$. The larger it is, the slower the Markov chain mixes. For our case, we require a slowly mixing VAR(1) process. We consider a bivariate example with $\phi_{\max} = 0.999$. We run five parallel deterministically initialized Markov chains with their starting points evenly distributed in the sample space. The correlation between the two components in the target distribution is very high for the chosen value of $\Phi$ and $\Omega$. As a result, it takes a long time for the Markov chain to explore the sample space significantly.

\begin{figure}[h]
\centering
   \includegraphics[width=.5\linewidth]{plots/var-acf_n1000.pdf}
     \includegraphics[width=.5\linewidth]{plots/var-acf_n10000.pdf} 
\caption{VAR(1). ACF (left) and G-ACF (right) for the second chain for $m=5$. (a): $n = 10^3$, not converged yet; (b): $n =  10^4$, converged. The red line marks the true ACF.}
\label{fig:var-acf}
\end{figure}

The locally and globally-centered autocorrelations for the second chain have been shown in Figure~\ref{fig:var-acf} for two different simulation sizes where the true ACF is shown by the red line. When the individual chains have not explored well, the local sample means have not converged to $\mu$. As a consequence, the single chain empirical ACF estimator severely underestimate the truth. Due to sufficiently dispersed starting values, G-ACF is closer to reality. In subfigure~\ref{subfig:var-acf_n1e4}, the convergence property of sample means has kicked in for each chain. Therefore, both the estimators provide equivalent results. Note that G-ACF reveals the true nature of ACF for almost ten times lesser chain length $n$

\begin{figure}[h]
    \centering
      \includegraphics[width = 2.2in]{plots/var-frob.pdf} 
      \includegraphics[width = 2.2in]{plots/var-ess.pdf}         
    % \begin{subfigure}{0.4\textwidth}
    %   \centering

    %   \caption{$log(\|\hat{\Sigma}\|_F)$}
    %   \label{subfig:var-frob}
    % \end{subfigure}
    % \begin{subfigure}{0.4\textwidth}
    %   \centering

    %   \caption{$\log(\widehat{\textrm{ESS}}/mn)$}
    %   \label{subfig:var-ess}
    % \end{subfigure}
    \caption{VAR(1). (a) Running plot for logarithm of Frobenius norm of A-SVE and G-SVE from $n = 500$ to $n = 10^5$. (b) Running plot for logarithm of $\widehat{\textrm{ESS}}/mn$ calculated using A-SVE and G-SVE from $n=500$ to $n=10^5$.}
    \label{fig:var-frob_n_ess}
\end{figure}

The quality of estimation of $\Sigma$ and $\text{ESS}/mn$ has been studied through convergence of - (a) $\log(\|\hat{\Sigma}_A\|_F)$ and $\log(\|\hat{\Sigma}_G\|_F)$ as $n$ increases and (b) $\log(\widehat{\textrm{ESS}}_A/mn)$ and $\log(\widehat{\textrm{ESS}}_G/mn)$ as $n$ increases. In practice, it is preferred to slightly overestimate the variance and underestimate the ESS than do otherwise. In Figure~\ref{fig:var-frob_n_ess}, both the running plots are shown along with the green horizontal line which marks the truth. We run the simulations for 50 replications for each value of $n$ and plot the average as well as standard errors. We run the simulations for a maximum chain length of $5 \times 10^4$ when the estimators seem to have almost converged. From Figure~\ref{subfig:var-frob}, it can be seen that for first $10000$ samples, A-SV estimates can be absurdly small giving false confidence in single chain estimates whereas G-SV gives a better understanding of reality. Similar comparative argument can can given for ESS.

\begin{table}[h]
    \centering
    \begin{tabular}{|c|ccccc|}
    \hline
$n$  &  1000  & 5000  & 10000  & 50000  & 100000 \\  \hline
A-SV  &    0.710 & 0.843 & .885 & .928 & .944 \\ 
G-SV  &    0.956 & 0.937 & .924 & .945 & .952 \\ \hline
    \end{tabular}
    \caption{VAR(1). Coverage probabilities at $95 \%$ nominal level using A-SVE and G-SVE.}
    \label{tab:var-coverage}
\end{table}

We also report the coverage probabilities for a $95\%$ confidence interval constructed using $\hat{\Sigma}_A$ and $\hat{\Sigma}_G$ because the true mean is known here. Table~\ref{tab:var-coverage} shows that for each sample size, the globally-centered SV estimator for variance gives better coverage than A-SVE. At $n=10^5$, both the estimators have converged and give equivalently good coverage probability.

@@

Our globally-centered estimators perform exceptionally better than the single-chain estimators in case of multimodal target distribution. To that end, we will use a bivariate bi-modal distribution introduced by \cite{gelman1991note} which has Gaussian conditional distributions in both directions. This allows us to sample parallel Markov chains using the Gibbs sampler. Let $x$ and $y$ be two random variable that are jointly distributed as 
%
\[
f(x, y) \propto \exp\left(-\dfrac{1}{2} \left[Ax^2y^2 + x^2 + y^2 -2Bxy  -2C_1x - 2C_2y  \right]\right)
\]

The conditional distribution of $x$ given $y$ and vice versa is a normal distribution given by:
%
\begin{align*}
    x_1 \mid x_2 &\sim N\left(\dfrac{Bx_2 + C_1}{Ax_2^2 + 1}, \dfrac{1}{Ax_2^2 + 1}\right)\\
    x_2 \mid x_1 &\sim N\left(\dfrac{Bx_1 + C_2}{Ax_1^2 + 1}, \dfrac{1}{Ax_1^2 + 1}\right)
\end{align*}

@@

    \caption{Boomerang. Contour plots of the target distributions  overlayed with scatter plots for two chains for Setting 1 (left) and Setting 2 (right).}
   \label{fig:boom-2D}
\end{figure}

We report results for two different bi-modal parameter settings in this example. Firstly, we use a carefully chosen parameterization of $A = 1,\; B = 3,\; C = 8$ wherein the two modes are well-separated with a very low connection (Setting-1, Figure~\ref{subfig:boom-2D_1_3_8}). Secondly, to examine the performance of G-SVE for a nicely mixing Markov chain, we use the parametrization of $A = 1, \; B = 10, \; C=7$ wherein the two modes are closer and well-connected (Setting-2, Figure~\ref{subfig:boom-2D_1_10_7}). We will make another point through this example. For a fast mixing Markov chain, the globally-centered and locally-centered estimators give equivalent results. Therefore, it is a better practice to globally center the chains in any situation. We sample five parallel deterministically initialized chains with starting points dispersed uniformly in the first quadrant. Finding the actual mean of this distribution in closed form is difficult. Therefore, we use numerical integration with fine tuning to calculate it.

 To visualize the sticky nature of Markov chains in Setting-1, we show a scatter plot of two Markov chains starting near the two modes for $n = 1000$ in Figure~\ref{fig:boom-2D}. For the first thousand samples, both the chains are oblivious of the existence of another mode in setting-1. Whereas in setting-2, the chains have mixed fairly well for just $n=1000$.

 In Figure \ref{fig:boom-acf_1_3_8}, the autocorrelations are severely underestimated by A-ACF for $n=1000$ because the chains have not jumped modes. Whereas, for $n=10000$, both ACF and G-ACF give almost indistinguishable results indicating that A-ACF and G-ACF have converged to the truth. We can observe in Figure~\ref{fig:boom-acf_1_10_7} that A-ACF and G-ACF give similar results for just $n=1000$ under simulation setting-2.

\begin{figure}[h]
    \centering
      \includegraphics[width = .30\textwidth]{plots/boom-ess_1_3_8_m5.pdf}
      \includegraphics[width = .30\textwidth]{plots/boom-ess_1_10_7_m5.pdf}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width = .30\textwidth]{plots/boom-frob_1_3_8_m5.pdf}  
    \includegraphics[width = .30\textwidth]{plots/boom-frob_1_10_7_m5.pdf}

    \caption{Boom: Running plot of $\log(\|\hat{\Sigma}_A\|_F)$ and $\log (\|\hat{\Sigma}_G\|_F)$ with $m = 5$ for Setting 1 (left) and Setting 2 (right).}
    \label{fig:boom-frob}
\end{figure}

The convergence of $\log \widehat{\textrm{ESS}}_G/mn$ and $\log \widehat{\textrm{ESS}}_A/mn$ as $n$ increases can be seen in Figure~\ref{fig:boom-ess}. We can see that in the beginning, A-SVE gives misleadingly higher estimates of ESS$/mn$ than G-SVE. This can cause us to stop the sampling before each chain jumps to the other mode. As a consequence, each chain will correspond to a uni-modal target distribution. Whereas, as expected, the ESS estimates for setting-2 are almost same. Similarly, $\|\hat{\Sigma}_G\|_F$ reaches the convergence point in less than half the time as $\|\hat{\Sigma}_G\|_F$; as evidenced in Figure~\ref{subfig:boom-frob1}. No significant difference can be observed for setting-2 (Figure~\ref{subfig:boom-frob2}).

\begin{table}[h]
\parbox{.45\linewidth}{
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline
 $n$ & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
 \hline
 & A-SV & G-SV & A-SV & G-SV \\
 \hline
 5000 & 0.595 &  0.700 & 0.402 &  0.640\\
 10000 & 0.563 &  0.665 & 0.59 &  0.739\\
 50000 & 0.775 &  0.814 & 0.807 &  0.864\\
 100000 & 0.847 &  0.864 & 0.884 &  0.902\\
\hline
\end{tabular}
\caption{Setting-1}
\label{tab:boom-coverage_1}
}
\hfill
\parbox{.45\linewidth}{
\centering
\begin{tabular}{|c|c|c|c|c|}
 \hline
 $n$ & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
 \hline
 & A-SV & G-SV & A-SV & G-SV \\
 \hline
 1000 &  0.856 &  0.868 & 0.895 &  0.910\\
 5000 & 0.921 &  0.925 & 0.910 &  0.915\\
 10000 & 0.928 &  0.93 & 0.919 &  0.926\\
 50000 & 0.943 &  0.944 & 0.951 &  0.952\\
\hline
\end{tabular}
\caption{Setting-2}
\label{tab:boom-coverage_2}
}
\end{table}

Using the numerical approximation of the true mean, we construct the $95\%$ confidence interval using A-SVE and G-SVE. We report the coverage probabilities for a 1000 replications at different sample sizes $n$. For both the simulation settings, we provide coverage probabilities for $m=2$ and $m=5$. Table \ref{tab:boom-coverage_1}, \ref{tab:boom-coverage_2} reports all these results. In setting-1, it can be observed that G-SVE gives higher coverage probability than A-SVE for all values of $n$. Whereas for setting-2, the results are almost similar indicating the equivalence of A-SVE and G-SVE.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width = .6\textwidth]{plots/sensor-trace_loc1.pdf}
    \caption{Sensor: Trace plots for $x$ (left) and $y$ (right) coordinate of sensor location-1.}
    \label{fig:sensor-trace}
\end{figure}

@@

\begin{figure}[h]
    \centering
      \includegraphics[width = .33\textwidth]{plots/sensor-acf_n5e3.pdf}\includegraphics[width = .33\textwidth]{plots/sensor-acf_n5e4.pdf}

    \caption{Sensor: ACF (orange) and G-ACF (blue) for individual chains (dotted lines) and average over all chains (solid line) for $n = 5000$ (left) and $n = 50000$ (right).}
    \label{fig:sensor-acf}
\end{figure}

>>>>

An important method of assessing the reliability of $\bar{\bar{Y}}$ in estimating $\mu_g$ is to calculate the effective sample size (ESS). ESS are number of independent and identically distributed samples that would yield the same Monte Carlo variability as this correlated sampler for estimating $\mu_g$. Let $|\cdot|$ denote determinant. A multiple chain version of the ESS as defined by \cite{vats2019multivariate} is
\[
\textrm{ESS} = mn \left(\dfrac{|\Upsilon(0)|}{|\Sigma|}\right)^{1/p}\, .
\]

@@

Our first example is one where the $\Upsilon$ and $\Sigma$ are available in closed-form, so we can compare quality of estimation against a known truth. Consider a $p$-dimensional VAR(1) process $\{X_t\}_{t \geq 1}$ such that
%
\[
X_t = \Phi X_{t-1} + \epsilon_t
\]
%
where $X_t \in \mathbb{R}^p$, $\Phi $ is a $p \times p $ matrix, $ \epsilon_t \overset{i.i.d.}{\sim} N(0, \Omega)$, and $\Omega$ is a positive definite $p \times p$ matrix. We fix $\Omega$ be a AR correlation matrix with parameter .9. The invariant distribution for this Markov chain is $N(0, \Psi)$, where $vec(\Psi) = (I_{p^2} - \Phi \times \Phi)^{-1} vec(W)$. We are interested in estimating the mean of the stationary distribution, so $g$ is the identity function.  For $k > 0$, the lag-$k$ autocovariance is $\Upsilon(k) = \Gamma(k) = \Phi^k\Psi$. The process satisfies a CLT for $\bar{X} = n^{-1} \sum_{t=1}^{n} X_t$ if the spectral norm of $\Phi$ is less than 1 \citep{10.2307/1427459} and the limiting covariance, $\Sigma$ is known in closed form \citep{dai:jon:2017}. We set $p = 2$ and set $\Phi$ such that its eigenvalues are .999 and .001. The resulting process is slowly mixing and allows us to highlight the difference in the estimation of ACvF.We further set $m = 5$ with starting values dispersed across the state space.  
\begin{figure}[htbp]
\centering
   \includegraphics[width=.5\linewidth]{plots/var-acf_n1000.pdf}
     \includegraphics[width=.5\linewidth]{plots/var-acf_n10000.pdf} 
\caption{VAR(1). ACF (left) and G-ACF (right) for the second chain for $m = 5$. (Top) $n = 10^3$  and (bottom) $n =  10^4$. The red line is the true ACF.}
\label{fig:var-acf}
\end{figure}

We compare the the locally and globally-centered autocorrelations against the truth. In Figure~\ref{fig:var-acf} are the estimated ACF plots for the first component of the second chain against the truth in red. For a run length of $10^3$ (top row), the commonly used locally centered ACF underestimates the true correlation structure giving a false sense of security about the mixing of the chain. The G-ACF, on the other hand, is much closer to the truth. This difference is negligible at the larger run length of $n = 10^4$ when each of the 5 chains have sufficiently explored the state space.

Since $\mu_g$ is known, we assess the performance of ASV and GSV by assessing coverage probabilities of $95\%$ Wald confidence regions over 1000 replications.  Table~\ref{tab:var-coverage} shows that for each sample size, the $\hat{\Sigma}_G$ results in close to nominal coverage probability, whereas $\hat{\Sigma}_A$ yields critically low coverage. The low coverage is a consequence of underestimating the autocovariances. It is only at the sample size of $n=10^5$ that $\hat{\Sigma}_A$ yields close to nominal coverage.

\begin{table}[htbp]
    \centering
    \small
    \begin{tabular}{|c|ccccc|}
    \hline
$n$  &  1000  & 5000  & 10000  & 50000  & 100000 \\  \hline
A-SV  &    0.710 & 0.843 & .885 & .928 & .944 \\ 
G-SV  &    0.956 & 0.937 & .924 & .945 & .952 \\ \hline
    \end{tabular}
    \caption{VAR(1). Coverage probabilities at $95 \%$ nominal level using A-SVE and G-SVE.}
    \label{tab:var-coverage}
\end{table}

The quality of estimation of $\Sigma$ and $\text{ESS}$ is assessed by running plots from 50 replications of run length 50000. 
 In Figure~\ref{fig:var-frob_n_ess}, we present running plots of $\log(\|\hat{\Sigma}\|_F)$ for both $\hat{\Sigma}_G$ and $\hat{\Sigma}_A$ and the running plots of $\log(\widehat{\text{ESS}})$ for both  $\widehat{\text{ESS}}_G$ and $\widehat{\text{ESS}}_A$. It is evident that the locally centered estimator of $\Sigma$ severely underestimates the truth, leading to an overestimation of ESS. The GSV estimator is able to estimate $\Sigma$ more accurately early on, safeguarding against early termination using ESS. 
\begin{figure}[htbp]
    \centering
      \includegraphics[width = 2.2in]{plots/var-frob.pdf} 
      \includegraphics[width = 2.2in]{plots/var-ess.pdf}         
    \caption{VAR(1). (Left) Running plot for logarithm of Frobenius norm of A-SV and G-SV.(Right) Running plot for logarithm of $\widehat{\textrm{ESS}}/mn$ using A-SV and G-SV.}
    \label{fig:var-frob_n_ess}
\end{figure}

@@

Consider the following family of bimodal bivariate distributions introduced by \cite{gelman1991note}, which term as a boomerang distribution. For $A \geq 0$ and $B, C  \in \mathbb{R}$, the target density is
%
\[
f(x, y) \propto \exp\left(-\dfrac{1}{2} \left[Ax^2y^2 + x^2 + y^2 -2Bxy  -2Cx - 2Cy  \right]\right)\,.
\]
We run a deterministic scan Gibbs sampler to sample from this target using the following full conditional densities
%
\begin{align*}
    x \mid y &\sim N\left(\dfrac{By + C}{Ay^2 + 1}, \dfrac{1}{Ay^2 + 1}\right)\\
    y \mid x &\sim N\left(\dfrac{Bx + C}{Ax^2 + 1}, \dfrac{1}{Ax^2 + 1}\right)\,.
\end{align*}

@@

    \caption{Boomerang. Top row is Setting 1 and bottom row is Setting 2. Contour plots of the target distributions  overlaid with scatter plots for two chains for both settings.  Locally-centered ACF (middle) and G-ACF (right) plots for one chain for $n = 1000$ with the blue line being the respectie ACF at $n = 10^4$.  }
   \label{fig:boom-2D}
\end{figure}

We consider two settings; in setting 1 we let
$A = 1,\; B = 3,\; C = 8$ which results in well-separated models. In setting 2, we let $A = 1, \; B = 10, \; C=7$ which yields in a boomerang shape for the contours. The contour plots for these two settings are in the left in Figure~\ref{fig:boom-2D}, overlaid with scatter plots of two parallel draws of the Gibbs sampler. Setting 2 is chosen specifically to illustrate that the locally and globally centered ACvFs perform similarly when the Markov chain moves freely across the state space.  {\color{red} what is m here?}

 For Setting 1, when the Markov chains have not been able to jump modes, locally-centered ACF severely underestimates autocorrelation. This is seen in the middle column in Figure \ref{fig:boom-2D}, where the locally-centered autocorrelations at $n=1000$ (histogram) are drastically different from the locally-centered autocorrelations at $n = 10^4$. Somewhere between $n = 1000$ and $n = 10^4$, the Markov chains jump modes and it is only then that the locally-centered ACFs provide better estimates. The G-ACFs,  on the other hand, produce similar ACF estimates at $n = 1000$ and $n = 10^4$ by measuring deviations about the global mean. For setting 2, both methods yield similar ACF estimates reinforcing our claim that there is much to gain by using G-ACvF and nothing to lose.

\begin{table}[h]
\parbox{.45\linewidth}{
\centering
\small
\begin{tabular}{|c|c|c|c|c|}
\hline
 $n$ & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
 \hline
 & A-SV & G-SV & A-SV & G-SV \\
 \hline
 5000 & 0.595 &  0.700 & 0.402 &  0.640\\
 10000 & 0.563 &  0.665 & 0.59 &  0.739\\
 50000 & 0.775 &  0.814 & 0.807 &  0.864\\
 100000 & 0.847 &  0.864 & 0.884 &  0.902\\
\hline
\end{tabular}
\caption{Setting-1}
\label{tab:boom-coverage_1}
}
\hfill
\parbox{.45\linewidth}{
\centering
\small
\begin{tabular}{|c|c|c|c|c|}
 \hline
 $n$ & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
 \hline
 & A-SV & G-SV & A-SV & G-SV \\
 \hline
 1000 &  0.856 &  0.868 & 0.895 &  0.910\\
 5000 & 0.921 &  0.925 & 0.910 &  0.915\\
 10000 & 0.928 &  0.93 & 0.919 &  0.926\\
 50000 & 0.943 &  0.944 & 0.951 &  0.952\\
\hline
\end{tabular}
\caption{Setting-2}
\label{tab:boom-coverage_2}
}
\end{table}

The true mean of the target distribution can be obtained using numerical approximation. Using this and both the A-SV and G-SV estimators, we construct $95\%$ confidence regions and report coverage probabilities for 1000 replications for both $m=2$ and $m=5$. Table \ref{tab:boom-coverage_1}, \ref{tab:boom-coverage_2} reports all  results. In setting 1, systematically, the G-SV estimator yields far superior coverage than the A-SV estimator for all values of $n$. Whereas for setting 2, the results are almost similar indicating the equivalence of A-SV and G-SV for fast mixing Markov chains.

\begin{figure}[h]
    \centering
      \includegraphics[width = .35\textwidth]{plots/boom-ess_1_3_8_m5.pdf}
      \includegraphics[width = .35\textwidth]{plots/boom-ess_1_10_7_m5.pdf}

@@

In Figure~\ref{fig:boom-ess} we present running plots of estimates of $\log \textrm{ESS}/mn$ for both setting 1 and setting 2. As the sample size increases, $\widehat{\text{ESS}}_G$ and  $\widehat{\text{ESS}}_A$ become closer, but early on for setting 1, $\widehat{\text{ESS}}_G$ estimates are much smaller giving more adequate estimates of ESS.

 % and $\log \widehat{\textrm{ESS}}_A/mn$ as $n$ increases can be seen in Figure~\ref{fig:boom-ess}. We can see that in the beginning, A-SVE gives misleadingly higher estimates of ESS$/mn$ than G-SVE. This can cause us to stop the sampling before each chain jumps to the other mode. As a consequence, each chain will correspond to a uni-modal target distribution. Whereas, as expected, the ESS estimates for setting-2 are almost same. Similarly, $\|\hat{\Sigma}_G\|_F$ reaches the convergence point in less than half the time as $\|\hat{\Sigma}_G\|_F$; as evidenced in Figure~\ref{subfig:boom-frob1}. No significant difference can be observed for setting-2 (Figure~\ref{subfig:boom-frob2}).

% \begin{figure}[h]
%     \centering
%     \includegraphics[width = .30\textwidth]{plots/boom-frob_1_3_8_m5.pdf}  
%     \includegraphics[width = .30\textwidth]{plots/boom-frob_1_10_7_m5.pdf}

%     \caption{Boom: Running plot of $\log(\|\hat{\Sigma}_A\|_F)$ and $\log (\|\hat{\Sigma}_G\|_F)$ with $m = 5$ for Setting 1 (left) and Setting 2 (right).}
%     \label{fig:boom-frob}
% \end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width = .32\textwidth]{plots/sensor-trace_loc1.pdf}
      \includegraphics[width = .32\textwidth]{plots/sensor-acf_n5e3.pdf}
      \includegraphics[width = .32\textwidth]{plots/sensor-acf_n5e4.pdf}    
    \caption{Sensor: Trace plots for $x$ (left) and $y$ (right) coordinate of sensor location-1.}
    \label{fig:sensor-trace}
\end{figure}

@@

% \begin{figure}[h]
%     \centering
%       \includegraphics[width = .33\textwidth]{plots/sensor-acf_n5e3.pdf}
%       \includegraphics[width = .33\textwidth]{plots/sensor-acf_n5e4.pdf}

%     \caption{Sensor: ACF (orange) and G-ACF (blue) for individual chains (dotted lines) and average over all chains (solid line) for $n = 5000$ (left) and $n = 50000$ (right).}
%     \label{fig:sensor-acf}
% \end{figure}
